---
title: "Clean butterfly behavioral data"
output:
  html_document:
    code_download: true
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
---

# Introduction

Much of the empirical data in the multistep relational abstraction paper is re-analysis of datasets from other researchers. The major exceptions are two datasets collected by people in this lab, both of which used the same artificial social network (i.e., the "butterfly" network, so named because it resembles a butterfly with its wings extended). Here, we're going to clean those two behavioral datasets.


# Initialize

Loading libraries and custom scripts...

```{r setup}
library(tidyverse)
library(here)
```


# Load & tidy data

## Random walks

This dataset was originally collected as pilot data for another set of (mostly unrelated) experiments, but we can reanalyze them and make them useful for answering our present set of questions.

The datafile `randomwalks.csv` contains 27 complete datapoints. Of these, 19 subjects were recruited from Prolific and completed 837 steps of a random walk in the learning task. The remaining 8 are in-lab pilots. One of them is (probably) from an in-lab pilot before putting the task online, and completed 837 steps of a random walk. The remaining 7 were collected after the Prolific study, and completed *twice* as many steps (1674) in the random walks.

The datafile `randomwalks2.csv` contains 33 complete datapoints. They are all in-lab subjects. In the first RandomWalks, subjects were allowed to take self-timed breaks between learning runs. In this second iteration, subjects were required to take a 10s break. We went back to having a 837-step random walk because doubling the number of steps didn't seem to lead to any appreciable increase in accuracy.

We'll first load in the raw data and do some preliminary cleaning. Warning messages about parsing errors can be safely ignored.

```{r walk-raw-data}
walk_data <- bind_rows(
  # RandomWalks
  here("data", "butterfly-raw", "random_walks", "randomwalks.csv") %>%
    read_csv(show_col_types = FALSE) %>%
    mutate(study = "randomwalks"),
  # RandomWalks2
  here("data", "butterfly-raw", "random_walks", "randomwalks2.csv") %>%
    read_csv(show_col_types = FALSE) %>%
    mutate(study = "randomwalks2")
) %>%
  # Data from Prolific or in-lab?
  mutate(
    pid = if_else(str_detect(responses, "^\"$"), NA_character_, responses)
  ) %>%
  fill(pid, .direction = "down") %>%
  mutate(data_source = if_else(str_length(pid) > 30, "prolific", "lab")) %>%
  # Renumber anonymous subjects
  rename(sub_id = run_id) %>%
  group_by(study, sub_id) %>%
  mutate(sub_id = cur_group_id()) %>%
  ungroup() %>%
  arrange(sub_id, trial_index)
```

This study also used text identifiers (e.g., "R1a") instead of numeric identifiers, so let's go ahead and create a crosswalk so that we can later work with numeric identifiers.

```{r node-id-crosswalk}
node_id_crosswalk <- walk_data %>%
  filter(trial_purpose == "walk_trial") %>%
  select(node_id_text = node_id) %>%
  distinct() %>%
  arrange(node_id_text) %>%
  mutate(node_id = row_number())
```

## Paired associates

In this study, note that data collection occurred in two "waves" as part of a larger-scale fMRI study. The first wave of data collection was intended to capitalize on some expiring grants. The second wave of data collection, several months later, collected the remaining subjects to reach the target sample size. Subjects from the first wave completed these tasks online using the `cognition.run` web service, and subjects from the second wave completed these tasks "locally" simply by running the jsPsych code in a browser. Due to this difference, data are formatted slightly differently in the two waves.

Warning messages about parsing errors can be safely ignored.

```{r pair-raw-data}
pair_data <- here(
  "data", "butterfly-raw", "paired_associates", "paired_associates_wave1.csv"
) %>%
  # Networked pairs, first wave
  read_csv(show_col_types = FALSE) %>%
  rename(sub_id = pid) %>%
  # Fix column types as much as possible
  mutate(
    across(
      where(is.character),
      ~if_else(str_detect(.x, "^\\\"$|^null$"), NA_character_, .x)
    )
  ) %>%
  type_convert(col_types = cols()) %>%
  # Fix subject numbering (experimenter error)
  mutate(sub_id = if_else(run_id == 11, 8, sub_id)) %>%
  # Add data from the second-wave subjects
  bind_rows(
    here("data", "butterfly-raw", "paired_associates") %>%
      fs::dir_ls(regexp = "paired_associates_pid_[[:digit:]]+\\.csv$") %>%
      map_dfr(read_csv, show_col_types = FALSE, .id = "filename") %>%
      mutate(
        across(
          where(is.character),
          ~if_else(str_detect(.x, "^\\\"$|^null$"), NA_character_, .x)
        )
      ) %>%
      type_convert(col_types = cols())
  ) %>%
  # Keep only what we want/need
  select(
    sub_id, trial_index, trial_type, trial_purpose,
    rt, response,
    from_id:friendship
  ) %>%
  # Make stimulus identifiers consistent
  mutate(
    across(
      c(from_face, to_face),
      ~str_remove(.x, "^stims/img/")
    )
  ) %>%
  # Make pretty
  arrange(sub_id, trial_index)
```


# Learning data

The random walk learning task comes in the form of a sequence, so we'll convert that into pairwise observations where each trial encodes which node we are coming `from` and which node we are going `to`.

```{r walk-learning}
walk_learn <- walk_data %>%
  filter(trial_purpose == "walk_trial") %>%
  select(
    study, data_source,
    sub_id, trial_index,
    walk_id, node_id, face_id
  ) %>%
  # Add numeric node IDs
  rename(node_id_text = node_id) %>%
  left_join(node_id_crosswalk, by = "node_id_text") %>%
  select(-node_id_text) %>%
  # In each run, a random walk stops at a random place
  # The next random walk picks up in another random place
  # So, need to make sure the SR isn't learning false relations
  group_by(sub_id, walk_id) %>%
  mutate(
    to = lead(node_id),
    to_face = lead(face_id)
  ) %>%
  rename(
    from = node_id,
    from_face = face_id
  ) %>%
  drop_na() %>%
  type_convert(col_types = cols()) %>%
  arrange(sub_id, walk_id, trial_index) %>%
  # Renumber trials
  group_by(sub_id) %>%
  mutate(trial_index = row_number()) %>%
  ungroup()
```

The paired associates learning task is already grouped into pairs.

```{r pair-learning}
pair_learn <- pair_data %>%
  filter(trial_purpose == "learning_trial") %>%
  select(
    sub_id, trial_index,
    from = from_id, to = to_id,
    from_face, to_face
  ) %>%
  # Renumber trials
  group_by(sub_id) %>%
  mutate(trial_index = row_number()) %>%
  ungroup()
```


# Memory data

The cleaning processes for the two studies are mostly the same, but look slightly different mostly because they used different versions of jsPsych (random walks used 6.x, paired associates used 7.x).

```{r walk-memory}
walk_mem <- walk_data %>%
  filter(str_detect(trial_purpose, "memory_")) %>%
  select(
    study, data_source,
    sub_id, trial_index, trial_purpose,
    from = from_id, to = to_id,
    from_face = from_img, to_face = to_img,
    friendship, key_press, rt
  ) %>%
  # Add numeric node IDs
  left_join(node_id_crosswalk, by = c("from"="node_id_text")) %>%
  left_join(node_id_crosswalk, by = c("to"="node_id_text")) %>%
  mutate(
    from = node_id.x,
    to = node_id.y
  ) %>%
  select(-starts_with("node_id.")) %>%
  # Convert javascript keycodes
  mutate(
    key_press = case_when(
      key_press == "83" ~ "s",
      key_press == "68" ~ "d",
      key_press == "70" ~ "f",
      key_press == "74" ~ "j",
      key_press == "75" ~ "k",
      key_press == "76" ~ "l"
    ),
    choice = case_when(
      # Yes/no
      key_press == "f" ~ 0,
      key_press == "j" ~ 1,
      # Confidence
      key_press == "s" ~ 1,
      key_press == "d" ~ 2,
      key_press == "k" ~ 3,
      key_press == "l" ~ 4
    )
  ) %>%
  # Get rid of quotation marks on confidence trials
  mutate(
    across(
      .cols = from_face:friendship,
      .fns = ~if_else(str_detect(.x, "^\\\"$"), NA_character_, .x)
    )
  ) %>%
  # Fill in from/to/friendship info on confidence trials
  fill(from:friendship, .direction = "down") %>%
  # Make choice/confidence part of the same row, rather than different rows
  select(-c(trial_index, key_press)) %>%
  pivot_wider(names_from = trial_purpose, values_from = c(choice, rt)) %>%
  rename(
    choice = choice_memory_resp,
    confidence = choice_memory_conf,
    rt_choice = rt_memory_resp,
    rt_confidence = rt_memory_conf
  ) %>%
  # Convert edge from yes/no to Boolean
  mutate(friendship = as.numeric(friendship == "yes")) %>%
  rename(edge = friendship) %>%
  # Fix data types
  type_convert(col_types = cols()) %>%
  # Sort
  mutate(
    from_sorted = if_else(from < to, from, to),
    to_sorted = if_else(from < to, to, from)
  ) %>%
  mutate(
    from = from_sorted,
    to = to_sorted
  ) %>%
  select(-c(from_sorted, to_sorted))
```

On to paired associates...

```{r pair-memory}
pair_mem <- pair_data %>%
  filter(str_detect(trial_purpose, "memory_")) %>%
  select(
    sub_id, trial_index, trial_purpose,
    from = from_id, to = to_id,
    from_face, to_face,
    friendship, response, rt
  ) %>%
  # Convert keys into choices
  mutate(
    choice = case_when(
      # Yes/no
      response == "f" ~ 0,
      response == "j" ~ 1,
      # Confidence
      response == "s" ~ 1,
      response == "d" ~ 2,
      response == "k" ~ 3,
      response == "l" ~ 4
    )
  ) %>%
  # Fill in from/to/friendship info on confidence trials
  fill(from:friendship, .direction = "down") %>%
  # Make choice/confidence part of the same row, rather than different rows
  select(-c(trial_index, response)) %>%
  pivot_wider(names_from = trial_purpose, values_from = c(choice, rt)) %>%
  rename(
    choice = choice_memory_resp,
    confidence = choice_memory_conf,
    rt_choice = rt_memory_resp,
    rt_confidence = rt_memory_conf
  ) %>%
  # Convert edge from yes/no to Boolean
  mutate(friendship = as.numeric(friendship)) %>%
  rename(edge = friendship)
```


# Trust prediction data

The trust prediction task was only a part of the paired associates study, and is straightforward to clean.

```{r pair-trust}
pair_trust <- pair_data %>%
  filter(trial_purpose == "trust_game") %>%
  select(sub_id, from = from_id, to = to_id, response, rt)
```


# Demographics

Demographics are only available for the paired associates study. They were not collected for the 

```{r pair-demographics}
pair_demographics <- pair_data %>%
  filter(trial_type == "survey") %>%
  select(sub_id, response) %>%
  # Wave 2 data
  bind_rows(
    here(
      "data", "butterfly-raw", "paired_associates",
      "paired_associates_wave2_demographics.csv"
    ) %>%
      read_csv(show_col_types = FALSE)
  ) %>%
  # Descend into regex hell
  separate(
    col = response,
    into = c("response", "gender"),
    sep = "(\\\"gender\\\")"
  ) %>%
  separate(
    col = response,
    into = c("response", "age"),
    sep = "(\\\"age\\\")"
  ) %>%
  separate(
    col = response,
    into = c(NA, "ethnicity"),
    sep = "(\\\"ethnicity\\\")"
  ) %>%
  # Clean up regex
  mutate(
    across(
      c(ethnicity, age, gender),
      ~str_remove_all(.x, "\\\"|\\[|\\]|,$|:|\\}")
    )
  ) %>%
  # Fix error in subject response; correct age noted on MRI safety form
  mutate(
    age = if_else(sub_id == 14, "20", age),
    age = as.numeric(age)
  ) %>%
  # Add data for a few subjects whose demographics are known, but not recorded
  bind_rows(
    tribble(
      ~sub_id, ~ethnicity, ~age, ~gender,
      1, "East Asian", 31, "Female",
      3, "South Asian", 29, "Female",
    )
  ) %>%
  arrange(sub_id)
```


# Export

```{r export-behavior}
if (dir.exists(here("data", "butterfly-behavior")) == FALSE) {
  dir.create(here("data", "butterfly-behavior"))
}

# Learning
walk_learn %>%
  write_csv(here("data", "butterfly-behavior", "walk_learn.csv"))

pair_learn %>%
  write_csv(here("data", "butterfly-behavior", "pair_learn.csv"))

# Memory
walk_mem %>%
  write_csv(here("data", "butterfly-behavior", "walk_mem.csv"))

pair_mem %>%
  write_csv(here("data", "butterfly-behavior", "pair_mem.csv"))

# Trust
pair_trust %>%
  write_csv(here("data", "butterfly-behavior", "pair_trust.csv"))

# Demographics
pair_demographics %>%
  write_csv(here("data", "butterfly-behavior", "pair_demographics.csv"))
```


# Session info

```{r session-info}
sessionInfo()
```

